### 2020-03-30 Thesis-Chapter2-Background.tex
Cite a few U.S. laws and attempted laws

Despite the failure of the Clipper Chip, the debate over access to strong encryption continued, primarily focused on
various key escrow proposals \cite{thompson_2015}. In 1996, two bills were introduced in the US Congress. In the Senate,
it was S.1726, the Pro-C0DE Act of 1996, to abolish the export controls on encryptions software \cite{burns_s1726_1996}.
In the House, it was HR.3011, the SAFE Act of 1996, to explicitly allow arbitrarily strong encryption for all legal
activity \cite{goodlatte_hr3011_1996}. Indeed, the SAFE Act went further, including ``provisions that would have
barred the government from creating a mandatory key escrow system and would also have removed export restrictions on
most generally available software and hardware containing encryption'' \cite{kehl_right_2015}. Zimmermann, the author of
PGP, who had by this time endured an investigation by the Customs Service for publishing his work, testified before the
Senate in favor of the Pro-C0DE Act \cite{zimmermann_1996}. The the Pro-C0DE Act passed, but the SAFE Act did not.

@@

\begin{itemize}
    \item The Clipper Chip \cite{press_1993} \cite{thompson_2015}
    \item The SAFE Act \cite{goodlatte_hr3011_1996}
    \item The EARN IT Act \cite{graham_s3398_2020}
    \item \dots
\end{itemize}

@@

\begin{itemize}
    \item Australia: in 2018 passed its Assistance and Access bill \cite{ag_2018} \cite{newman_2018}
    \item UK: Investigatory Powers Act \cite{legislature_2016}
    \item EU: GDPR
    \item China: \cite{donahue_comparative_2018}
    \item Israel: \cite{donahue_comparative_2018}
    \item Japan, Korea? -- can't find anything
    \item \dots General, see \cite{budish_encryption_2018}
\end{itemize}

>>>>

Despite the failure of the Clipper Chip, the debate over access to strong encryption continued, primarily focused on
various key escrow proposals \cite{thompson_2015}. In 1996, two bills were introduced in the US Congress. In the Senate,
it was S.1726, the Pro-C0DE Act of 1996, to abolish the export controls on encryption software \cite{burns_s1726_1996}.
In the House, it was HR.3011, the SAFE Act of 1996, to explicitly allow arbitrarily strong encryption for all legal
activity \cite{goodlatte_hr3011_1996}. Indeed, the SAFE Act went further, including ``provisions that would have
barred the government from creating a mandatory key escrow system and would also have removed export restrictions on
most generally available software and hardware containing encryption'' \cite{kehl_right_2015}. Zimmermann, the author of
PGP, who had by this time endured an investigation by the Customs Service for publishing his work, testified before the
Senate in favor of the Pro-C0DE Act \cite{zimmermann_1996}. 
% TODO: "The the Pro-C0DE Act passed, but the SAFE Act did not." -- WRONG! Neither passed, this was also achieved by executive order!

@@

\begin{itemize}
    \item The Clipper Chip \cite{press_1993} \cite{thompson_2015}
    \item The SAFE Act \cite{goodlatte_hr3011_1996}
    \item Encrypted Communications Privacy Act (mix of SE protection and EA guidelines?) \cite{leahy_s376_1997}
    \item Encryption Protects the Rights of Individuals from Violation and Abuse in CYberspace (E-PRIVACY) Act
        (like above?) \cite{ashcroft_s2067_1998}
    \item Encryption for the National Interest Act and Tax Relief for Responsible Encryption Act (introduced by same rep
        on same day) \cite{goss_hr2616_1999} \cite{goss_hr2617_1999}
    \item Compiance with Court Orders Act of 2016 (discussion draft) \cite{burr_2016}
    \item The Secure Data Act (federal SE protections) \cite{lofgren_hr5823_2018}
    \item The ENCRYPT Act (state SE protections) \cite{lieu_hr4170_2019}
    \item The EARN IT Act \cite{graham_s3398_2020}
    \item \dots
\end{itemize}

@@

\begin{itemize}
    \item Australia: in 2018 passed its Assistance and Access bill \cite{ag_2018} \cite{newman_2018}
    \item UK: Investigatory Powers Act \cite{legislature_2016}
    \item EU: GDPR \cite{parliament_2016}
    \item China: \cite{donahue_comparative_2018}
    \item Israel: \cite{donahue_comparative_2018}
    \item Japan, Korea? -- can't find anything
    \item \dots General, see \cite{budish_encryption_2018}
\end{itemize}
